### 2019-10-10 tim-lucas-model-ensembles.tex
Start writing results.

>>>>

Table \ref{t:results} gives the correlation between observed and held out data (under random and spatially cross-validation) for models that use environmental covariates only, local machine learning models only and a combination of the two.
Many of the differences in performance are rather marginal.
Overall, in only one case (random cross-validation in Senegal) is Enviro the best performing model while under spatially cross-validation in Senegal Enviro and Envir + ML\textsubscript{l} perform equally well.
Of the remaining six cases, in three cases ML\textsubscript{l} performs best and in three cases Envir + ML\textsubscript{l} performs best.
The greatest benefits in predictive performance occur under spatial cross validation and in the cases when the Enviro model is particularly poor.

Table \ref{t:results2} gives the correlation between observed and held out data (under random and spatially cross-validation) for models that use environmental covariates only, global machine learning models only and a combination of the local and global machine learning models.
In five cases, Enviro is the best or tied best performing model.
In only one case in the ML\textsubscript{g} model the best.
Comparing across Tables \ref{t:results} and \ref{t:results2} we can see that ML\textsubscript{g} is never the best performing model.
In only three cases (Spatial Colombia, Spatial Senegal and Spatial Indonesia) does ML\textsubscript{g} outperform ML\textsubscript{l}.
